---
title: "Analysis Blinding Versus Preregistration - H4"
output: html_document
---

## Analysis conducted on the unblinded version of the data
 
Hypothesis 4: Analysis teams in the preregistration condition should(1) deviate more often from their planned analysis than analysis teams in the blinding condition and (2) when they deviate from their analysis plan, analysis teams in the preregistration condition should deviate on more items than analysis teams in the blinding condition. We will test this hypothesis against the null hypothesis that both groups (1) deviate the same number of times from their analysis plan and (2) when they deviate from their analysis plan they do so for the same number of items.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rethinking)
library(bridgesampling)
library(rstan)
library(bayesplot)
fixed_seed <- 2021 # set seed for reproducibility purposes

```

```{r data}
datafile <- 'data/data_prereg_blinding_unblinded.csv' # specify correct path
dat <- read.csv(file = datafile, header=T)
```

## Stan Model

```{r stanmodel, message=FALSE, warning=FALSE, results='hide'}
dat$cond <- as.numeric(as.factor(dat$condition)) - 1
datalist <- list(N = nrow(dat), 
                 y = dat$deviation_count)
  
m0 <- rstan::stan(file ="h4_m0.stan",
                  data = datalist,
                  seed = fixed_seed,
                  iter = 10000,
                  warmup = 1000,
                  cores = 4)

datalist <- list(N = nrow(dat),
                 y = dat$deviation_count,
                 x = dat$cond)
m1 <- rstan::stan(file ="h4_m1.stan",
                  data = datalist,
                  seed = fixed_seed,
                  iter = 10000,
                  warmup = 1000,
                  cores = 4)

# bridge sampling Bayes factor
set.seed(fixed_seed)
m0_bridge <- bridgesampling::bridge_sampler(m0, seed = fixed_seed)
set.seed(fixed_seed)
m1_bridge <- bridgesampling::bridge_sampler(m1, seed = fixed_seed)
bf_e0 <- bridgesampling::bf(m1_bridge, m0_bridge)
```


```{r output}
# unconditional encompassing method Bayes factor
samp <- rstan::extract(m1)
post <- mean(samp$bp<0 & samp$bl>0)
prior <- 0.5^2
bf_re <- post/prior 

bf_r0 <- bf_e0$bf * bf_re
```

## Results 

```{r results}
bf_r0
sum(dat$deviation_count[dat$condition == 'blinding'] == 0)
sum(dat$deviation_count[dat$condition == 'preregistration'] == 0)

p_nodeviation_prereg <- logistic(median(samp[['ap']]) + median(samp[['bp']])) 
p_nodeviation_blinding <- logistic(median(samp[['ap']])) 
lambda_deviations_prereg <- exp(median(samp[['al']]) + median(samp[['bl']])) 
lambda_deviations_blinding <- exp(median(samp[['al']])) 
```

### Descriptives ###

```{r descriptives}
# proportion deviation in preregistration condition
mean(dat[dat$condition=='preregistration',]$deviation_count > 0)
# proportion deviation in blinding condition
mean(dat[dat$condition=='blinding',]$deviation_count > 0)
# average number of deviations when deviated in preregistration condition
# estimate includes possibility that teams report 0 deviations
mean(dat$deviation_count[dat$condition=='preregistration' & dat$deviation_count > 0])
# average number of deviations when deviated in blinding condition
# estimate includes possibility that teams report 0 deviations
mean(dat$deviation_count[dat$condition=='blinding' & dat$deviation_count > 0])

### Model Estimates ###
# probability of deviation in preregistration condition
round(1 - (p_nodeviation_prereg + (1 - p_nodeviation_prereg)*exp(-lambda_deviations_prereg)), 2)
# probability of deviation in blinding condition
round(1 - (p_nodeviation_blinding + (1 - p_nodeviation_blinding)*exp(-lambda_deviations_blinding)), 2)
  
```

```{r traceplots}
mcmc_trace(m1, pars = c("ap","al","bp","bl"))
```

## Robustness Check

```{r robustbridge, message=FALSE, warning=FALSE, results='hide'}
set.seed(fixed_seed)
m0_bridge2 <- bridgesampling::bridge_sampler(m0, seed = fixed_seed, repetitions=20)
set.seed(fixed_seed)
m1_bridge2 <- bridgesampling::bridge_sampler(m1, seed = fixed_seed, repetitions=20)
bf2_e0 <- bridgesampling::bf(m1_bridge2, m0_bridge2)
```

```{r robustoutput}
bf2_r0 <- bf2_e0$bf * bf_re
bf2_r0
```



