---
title: "Preregistered Analysis MARP"
author: "Suzanne Hoogeveen"
date: "11/18/2021"
output: pdf_document
---

Here, we report the results of our own preregistered analysis for the MARP data. 
The preregistration can be found at \url{https://osf.io/zyu8c/}. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("brms")
library("dplyr")
library("ggplot2")
library("ggrepel")
library("papaja")
```

# Prepare Data 

## Load data

```{r load-data}
dat <- read.csv("data/MARP_data.csv")
```

## Preprocess data

- exclude attention check failures
- create averages of the religiosity items (item 1, 2, 3, 5, 6, 7) and of the cultural norms items (item 1 and 2). 

```{r preprocess}
# exclude attention check failures
dat <- dat[dat$attention_check==1,] 
# create means for religiosity and cultural norms (all rel items except item 4)
dat$rel_mean <- rowMeans(dat[,grepl('rel_', colnames(dat))&colnames(dat)!="rel_4"]) 
dat$cnorm_mean <- rowMeans(dat[,c("cnorm_1","cnorm_2")])
```

## Standardize variables 

- standardize predictors, outcome, and continuous covariates ('age' is centered and rescaled as decades to facilitate interpretation)

```{r standardize-variables}
std.cols <- c('ses', 'education', 'rel_mean', 'cnorm_mean','wb_overall_mean')
dat[,std.cols] <- apply(dat[,std.cols], 2, function(x) scale(x, center = T, scale = T)[,1])
dat$age <- scale(dat$age, center=T, scale=F)[,1]/10
```

```{r select-variables}
analysis.cols <- c('ses', 'education', 'age', 'gender', 'rel_mean', 'cnorm_mean',
                   'wb_overall_mean', 'gdp_scaled')
dat <- dat[complete.cases(dat[,analysis.cols]),]
```

# Main Models

Note that it takes quite a while to run the code and get the Stan models. 

## Settings

```{r settings-brms}
iterations = 20000
warmup = 5000
chains = 4
```

## Hypothesis 1: is there a positive association between religiosity and well-being? 

```{r brms-h1, cache=TRUE, results='hide', error=FALSE, message=FALSE, warning=FALSE}
m0 <- brm(data = dat, family = gaussian(),
          formula = wb_overall_mean ~ 1 + age + gender + ses + education + (1 | country),
          prior = c(prior(normal(0, 10), class = Intercept),
                    prior(normal(0, 1), class = b),
                    prior(cauchy(0, 2), class = sd),
                    prior(cauchy(0, 10), class = sigma)),
          save_pars = save_pars(all = TRUE),
          iter = iterations, warmup = warmup, chains = chains, cores = 4, seed = 2021)

m1 <- brm(data = dat, family = gaussian(),
          wb_overall_mean ~ 1 + age + gender + ses + education + rel_mean + (1 + rel_mean | country),
          prior = c(prior(normal(0, 10), class = Intercept),
                    prior(normal(0, 1), class = b),
                    prior(cauchy(0, 2), class = sd),
                    prior(cauchy(0, 10), class = sigma),
                    prior(lkj(4), class = cor)),
          save_pars = save_pars(all = TRUE), 
          iter = iterations, warmup = warmup, chains = chains, cores = 4, seed = 2021)
```

```{r h1-results, cache=TRUE, message=FALSE, warning=FALSE}
print(summary(m1), digits=3)

# coefficients for the religiosity predictor 
summary(m1)$fixed['rel_mean',]

# Bayes factor for the inclusion of religiosity as a varying effect
bf10 <- bayes_factor(m1,m0)
bf10

# Posterior model probability
pp10 <- post_prob(m1,m0)
pp10
```

For research question 1, we find strong evidence that religiosity is positively related to well-being: BF$_{10}=$ `r printnum(bf10[1], format="g")`, posterior model probability is `r printnum(pp10[1])` for $\mathcal{M}_1$ and `r printnum(pp10[2])` for $\mathcal{M}_0$, the standardized estimate (beta) of the religiosity coefficient is `r printnum(summary(m1)$fixed['rel_mean','Estimate'], digits=3)`, 95% credible interval [`r printnum(summary(m1)$fixed['rel_mean','l-95% CI'], digits=3)`, `r printnum(summary(m1)$fixed['rel_mean','u-95% CI'], digits=3)`]. 

```{r h1-plot, echo=FALSE, fig.height=9}
countries <- unique(dat$country)
rbind(coef(m1)$country[, , 1],
      coef(m1)$country[, , 2]) %>% 
  as_tibble() %>% 
  mutate(param   = c(paste("Intercept", countries), paste("religiosity", countries)),
         reorder = c(24:1, 48:25)) %>% 

  # plot
  ggplot(aes(x = reorder(param, reorder))) +
  geom_hline(yintercept = 0, linetype = 3, color = "#8B9DAF") +
  geom_pointrange(aes(ymin = Q2.5, ymax = Q97.5, y = Estimate, color = reorder < 25),
                  shape = 20, size = 3/4) +
  scale_color_manual(values = c("#394165", "#A65141")) +
  xlab(NULL) +
  coord_flip() +
  theme_apa() +
  ggtitle("Estimated effect of individual religiosity on well-being and\nintercepts per country") +
  theme(legend.position = "none",
        axis.ticks.y    = element_blank(),
        axis.text.y     = element_text(hjust = 0))
```

## Hypothesis 2: does the association between religiosity and well-being depend on cultural norms of religion? 

```{r brms-h2, cache=TRUE, results='hide', error=FALSE, message=FALSE, warning=FALSE}
m02 <- brm(data = dat, family = gaussian(),
          formula = wb_overall_mean ~ 1 + age + gender + ses + education + rel_mean + 
            cnorm_mean + gdp_scaled + (1 + rel_mean | country),
          prior = c(prior(normal(0, 10), class = Intercept),
                    prior(normal(0, 1), class = b),
                    prior(cauchy(0, 2), class = sd),
                    prior(cauchy(0, 10), class = sigma),
                    prior(lkj(4), class = cor)),
          save_pars = save_pars(all = TRUE),
          iter = iterations, warmup = warmup, chains = chains, cores = 4, seed = 2021)

m2 <- brm(data = dat, family = gaussian(),
          formula = wb_overall_mean ~ 1 + age + gender + ses + education + rel_mean + 
            cnorm_mean + gdp_scaled + rel_mean:cnorm_mean + (1 + rel_mean | country),
          prior = c(prior(normal(0, 10), class = Intercept),
                    prior(normal(0, 1), class = b),
                    prior(cauchy(0, 2), class = sd),
                    prior(cauchy(0, 10), class = sigma),
                    prior(lkj(4), class = cor)),
          save_pars = save_pars(all = TRUE), 
          iter = iterations, warmup = warmup, chains = chains, cores = 4, seed = 2021)
```

```{r h2-results, cache=TRUE, message=FALSE, warning=FALSE}
print(summary(m2), digits=3)

# coefficients for the religiosity predictor 
summary(m2)$fixed['rel_mean:cnorm_mean',]

# Bayes factor for the inclusion of religiosity as a varying effect
bf20 <- bayes_factor(m2,m02)
bf20

# Posterior model probability
pp20 <- post_prob(m2,m02)
pp20
```

For research question 2, we find strong evidence that the association between religiosity and well-being depends on the cultural norms of religion within a country: BF$_{10}=$ `r printnum(bf20[1])`, posterior model probability is `r printnum(pp20[1])` for $\mathcal{M}_2$ and `r printnum(pp20[2])` for the corresponding $\mathcal{M}_0$, the standardized estimate (beta) of the religiosity-by-cultural norms interaction effect is `r printnum(summary(m2)$fixed['rel_mean:cnorm_mean','Estimate'], digits=3)`, 95% credible interval [`r printnum(summary(m2)$fixed['rel_mean:cnorm_mean','l-95% CI'], digits=3)`, `r printnum(summary(m2)$fixed['rel_mean:cnorm_mean','u-95% CI'], digits=3)`]. 


```{r h2-plot, echo=FALSE}
countries <- unique(dat$country)
norms <- dat %>% group_by(country) %>% summarise(mean=mean(cnorm_mean))
coef(m1)$country[, , 2] %>%
  as_tibble() %>%
  mutate(country = countries, 
         norms = norms$mean) %>% 

  # plot
  ggplot(aes(x = norms, y = Estimate)) +
  scale_x_continuous(limits = c(-1,1.5)) +
  geom_point() +
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5)) +
  geom_label_repel(aes(label=country)) + 
  ylab("Religiosity effect (estimated coefficient)") + 
  xlab("Cultural norms of religiosity (observed)") +
  theme_apa() +
  ggtitle("Country-level association between observed cultural norms of religion \nand the estimated effect of individual religiosity on well-being") +
  theme(legend.position = "none",
        axis.ticks.y    = element_blank(),
        axis.text.y     = element_text(hjust = 0))
```
